Learning From Massive Weakly Labeled Data for Visual Classification

### 2014-11-14 paper.tex
Modify experiments and figures

\section{Label Noise Model} % (fold)
\label{sec:label_noise_model}
We target on the problem of learning a classifier from a set of weakly labeled image data. To be specific, we have a weakly labeled dataset $\mathcal{D}_w=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes. Based on previous analysis of the noise types, we describe how the weak label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}. Despite the observed image $\vec{x}$ and the weak label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the ground truth and the type of label noise, respectively. Both $\tilde{\vec{y}}$ and $\vec{y}$ are $L$-dimensional binary random variables in 1-of-$L$ fashion, \ie, only one element is equal to 1 while others are all 0.

@@

On the other hand, the latent variable $\vec{z}$ representing label noise type is also an 1-of-3 binary random variable. We assign three semantic meanings to each possible state of $\vec{z}$:
\begin{enumerate}
    \item The weak label is noise free, \ie, $\tilde{\vec{y}}$ should be equal to $\vec{y}$
    \item The weak label suffers from a pointless noise, \ie, $\tilde{\vec{y}}$ can take any possible value other than $\vec{y}$
    \item The weak label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are easily confused with $\vec{y}$
\end{enumerate}

Following this assignment rule, we define the conditional probability of the weak label by
\begin{equation} \label{eq:likelihood}
    p(\tilde{\vec{y}}|\vec{y},\vec{z}) = \begin{cases}
        \mat{I}\vec{y} & \text{if } \vec{z}_1 = 1 \\
        \frac{1}{L-1}(\mat{U} - \mat{I})\vec{y} & \text{if } \vec{z}_2 = 1 \\
        \mat{C}\vec{y} & \text{if } \vec{z}_3 = 1
    \end{cases}
\end{equation}
where $\mat{I}$ is the identity matrix, $\mat{U}$ is the unit matrix (all the elements are one), and $\mat{C}$ is a sparse stochastic matrix with $\mathrm{tr}(\mat{C})=0$ and $\mat{C}_{ij}$ denoting the confusion probability between class $i$ and $j$. Then we can derive from Figure~\ref{fig:noise_pgm} the joint distribution of $\tilde{\vec{y}}, \vec{y}$ and $\vec{z}$ conditioning on $\vec{x}$:
\begin{equation} \label{eq:joint_distribution}
  p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}) = p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{y} | \vec{x}) p(\vec{z} | \vec{x})
\end{equation}

@@

To illustrate the relations between weak label and ground truth, we can derive their conditional probability from Eq~\ref{eq:joint_distribution} by
\begin{equation}
    p(\tilde{\vec{y}} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}}, \vec{z} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{z} | \vec{x})
\end{equation}
which can be interpreted as a mixture model. Given an input image $\vec{x}$, the conditional probability $p(\vec{z} | \vec{x})$ can be seen as the prior of each mixture component. This makes a key difference between our work and~\cite{sukhbaatar2014learning}, where they assume $\tilde{\vec{y}}$ is conditionally independent with $\vec{x}$ if $\vec{y}$ is given. All the images share a same noise model in~\cite{sukhbaatar2014learning}, while in our approach each data sample has its own.

@@

For any probability distribution $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})$, we can derive a lower bound of the incomplete log-likelihood by
\begin{equation}
\begin{aligned}
    \log p(\tilde{\vec{y}} | \vec{x}; \theta) &= \log \sum_{\vec{y},\vec{z}} p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
    &\geq \sum_{\vec{y},\vec{z}} q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) \log \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)}{q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})}
\end{aligned}
\end{equation}
\textbf{E-Step} The difference between $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$ and its lower bound is the Kullback-Leibler divergence $\mathrm{KL}\left(q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) || p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)\right)$, which is equal to zero if and only if $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)$. Therefore, in each iteration $t$ of the E-Step, we first compute the posterior of latent variables using current parameters $\theta^{(t)}$:
\begin{multline} \label{eq:posterior}
    p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) = \frac{p(\tilde{\vec{y}} | \vec{y}, \vec{z}, \vec{x}; \theta^{(t)})}{p(\tilde{\vec{y}} | \vec{x}; \theta^{(t)})} \\
    = \frac{p(\tilde{\vec{y}}|\vec{y},\vec{z};\theta^{(t)}) p(\vec{y}|\vec{x};\theta^{(t)}) p(\vec{z}|\vec{x};\theta^{(t)})}{\sum_{\vec{y}',\vec{z}'} p(\tilde{\vec{y}}|\vec{y}',\vec{z}';\theta^{(t)}) p(\vec{y}'|\vec{x};\theta^{(t)}) p(\vec{z}'|\vec{x};\theta^{(t)})}
\end{multline}
Then the expected complete log-likelihood can be written as
\begin{equation}
    Q(\theta; \theta^{(t)}) = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)
\end{equation}
\textbf{M-Step} Since deep neural networks are exploited to model the probability $p(\vec{y}|\vec{x};\theta_1)$ and $p(\vec{z}|\vec{x};\theta_2)$, we perform gradient ascent on $Q$:
\begin{multline}
    \frac{\partial Q}{\partial \theta} = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta} \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
    = \sum_{\vec{y},\vec{z}} w(\vec{y},\vec{z}) \left\{\frac{\partial}{\partial \theta_1}\log p(\vec{y}|\vec{x};\theta_1) + \frac{\partial}{\partial \theta_2} \log p(\vec{z}|\vec{x};\theta_2) \right\}
\end{multline}
where $w(\vec{y},\vec{z}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)})$ can be treated as the weights of each pair of latent variables.

@@

\subsection{Confusion Estimation} % (fold)
\label{sub:confusion_estimation}
Notice that we do not set parameters to the conditional probability $p(\tilde{\vec{y}}|\vec{y},\vec{z})$ in Eq~\eqref{eq:likelihood} and keep it unchanged during the learning process. Because without other regularizations, learning all the three parts could lead to trivial solutions. For example, the network will always predict $\vec{y}_1 = 1$, $\vec{z}_3 = 1$, and the matrix $\mat{C}$ is learned to make $\mat{C}_{1i} = 1$ for all $i$. To avoid this degeneration, we choose to give $\mat{C}$ a good estimation while let the deep model learn to predict $p(\vec{y} | \vec{x})$ and $p(\vec{z} | \vec{x})$ for each input image.

We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_s = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both strong label and weak label. As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
\begin{equation}
    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N p(\tilde{\vec{y}}^{(N)}|\vec{y}^{(N)},\vec{z}^{(N)})
\end{equation}
Obviously, sample $i$ contributes nothing to the optimal $\mat{C}^*$ if $\vec{y}^{(i)}$ and $\tilde{\vec{y}}^{(i)}$ are equal. So that we ignore those samples and reinterpret the problem in another form by exploiting Eq~\ref{eq:likelihood}:
\begin{equation}
\begin{aligned}
\max_{\mat{C},\vec{t}} \quad & E=\sum_{i=1}^{N'} \log \alpha^{\vec{t}_i} + \log (\tilde{\vec{y}}^{(i)T} \mat{C} \vec{y}^{(i)})^{1-\vec{t}_i}\\
\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } K\times K \\
                    & \vec{t} \in \{0,1\}^{N'}
\end{aligned}
\end{equation}
where $\alpha=\frac{1}{L-1}$ and $N'$ is the number of remaining samples. The semantic meaning of the above formulation is that we need to assign each $(\vec{y},\tilde{\vec{y}})$ pair the optimal noise type, while finding the optimal $\mat{C}$ simultaneously.

@@

\section{Deep Learning From Weak Labels} % (fold)
\label{sec:weak_label_deep_learning}
\begin{figure*}
\begin{center}
\includegraphics[width=0.9\linewidth]{figure/diagram.pdf}
\end{center}
\caption{System diagram of our proposed method. Two CNNs are exploited to predict object class $p(\vec{y}|\vec{x})$ and noise type $p(\vec{z}|\vec{x})$ respectively. A label noise model layer infers the ground truths according to CNNs' results and the observed weak label. The ground truth is then used to supervise the CNNs. A separate strongly labeled dataset is also utilized to prevent the model from drifting away.}
\label{fig:framework}
\end{figure*}

We integrate the proposed label noise model into a deep learning framework. As demonstrated in Figure~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs. Moreover, we append a weak-label-loss layer at the end, which takes as input the CNNs' prediction scores and the observed weak label. Stochastic Gradient Descent (SGD) with backpropagation technique is used to approximately optimize the whole network. In each forward pass, the weak-label-loss layer computes the posterior of latent variables according to Eq~\eqref{eq:posterior}. While in the backward pass, it computes the weighted sum of gradients with respect to $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$, thus the errors can be further propagated back. The forward procedure is summarized in Algorithm~\ref{alg:forward}, and the backward pass for computing gradient with respect to $p(\vec{y}|\vec{x})$ is illustrated in Algorithm~\ref{alg:backward}.

\begin{algorithm}
    \SetKwData{Sum}{sum}
    \SetKwFunction{Softmax}{Softmax}\SetKwFunction{Q}{Q}
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}

    \Input{Observed weak label vector $\tilde{\vec{y}}$ of size $N$}
    \Input{Object class scores matrix $Y$ of size $N \times L$}
    \Input{Noise type scores matrix $Z$ of size $N \times 3$}
    \Output{Posterior probability matrix $P$ of size $L \times 3$}
    \BlankLine

    $P_y \leftarrow$ \Softmax{$Y$}\;
    $P_z \leftarrow$ \Softmax{$Z$}\;
    \BlankLine

    \emph{\Q is the function that implements Eq~\eqref{eq:likelihood}}\;
    \BlankLine

    \For {$i \leftarrow 1$ \KwTo $N$} {
        \Sum $\leftarrow 0$\;
        \For {$j \leftarrow 1$ \KwTo $L$} {
            \For {$k \leftarrow 1$ \KwTo $3$} {
                $P[i,j,k] \leftarrow P_y[i,j] \times P_z[i,k] \times$ \Q{$\tilde{\vec{y}}$,j,k}\;
                \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
            }
        }
        $P[i,:,:] \leftarrow P[i,:,:] /$ \Sum\;
    }

    \caption{Forward pass}
    \label{alg:forward}
\end{algorithm}
\begin{algorithm}
    \SetKwData{Sum}{sum}
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}

    \Input{Object class scores matrix $Y$ of size $N \times L$}
    \Input{Posterior probability matrix $P$ of size $L \times 3$}
    \Output{Gradient matrix $\Delta_Y$ of size $N \times L$}
    \BlankLine

    \For {$i \leftarrow 1$ \KwTo $N$} {
        \For {$j \leftarrow 1$ \KwTo $L$} {
            \Sum $\leftarrow 0$\;
            \For {$k \leftarrow 1$ \KwTo $3$} {
                \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
            }
            $\Delta_Y[i,:] \leftarrow \Delta_Y[i,:] + $ \Sum $\times Y[i,:]$\;
            $\Delta_Y[i,j] \leftarrow \Delta_Y[i,j] - $ \Sum\;
        }
    }

    \caption{Backward pass for computing gradient w.r.t. object class scores}
    \label{alg:backward}
\end{algorithm}

Directly training the whole network with random initialization is impractical, because the posterior computation could be totally wrong. Therefore, we need to pretrain each CNN component with strongly supervised data. Gathering ground truth object classes is straight forward, since we can just manually label some images by expert. The resulting strongly labeled dataset $\mathcal{D}_s$ can be directly used for training the network that predicts $p(\vec{y}|\vec{x})$. On the other hand, although off-the-shelf supervision for $p(\vec{z}|\vec{x})$ is not available, we can heuristically generate some data by utilizing the images having both strong and weak labels. For each sample, we choose as ground truth the $\vec{z}$ that maximizes the likelihood in Eq~\eqref{eq:likelihood}.

After both the CNN components are properly pretrained, we can start training the whole network with massive weakly labeled data. However, some practical issues need to be further discussed. First, if we merely use weak data, we will lose precious knowledge that we have gained before and the model could be drifted. Therefore, we need to mix strongly label data together in to our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNN components. Then each CNN receives two kinds of gradients, one is from the strongly supervised data and the other is from the weakly supervised data. We denote them by $\Delta_s$ and $\Delta_w$, respectively. A potential problem is that $|\Delta_s| \ll |\Delta_w|$, because strongly labeled data is much less than the weak data. To deal with this problem, we bootstrap the strongly labeled data $\mathcal{D}_s$ to half amount of the weak data $\mathcal{D}_w$. This upsampling process brings another advantage --- the gradients we calculated in each mini-batch are much more stable.

Our proposed model has the ability to figure out the ground truth label given the image and its weak label. From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how confusing is the input image itself. Label Propagation method~\cite{zhu2002learning} explicitly uses the first kind of information, while we implicitly capture it with a discriminative deep model. Meanwhile, we exploit the second kind of information to bridge the semantic gap between the image and its possible noisy labels.
% section weak_label_deep_learning (end)

@@

In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_s$), validation and testing sets. Meanwhile remaining data construct the weakly labeled training dataset $\mathcal{D}_w$. Notice that near duplicate images are removed from training datasets $\mathcal{D}_s$ and $\mathcal{D}_w$ to ensure that our testing protocol is reliable. The size of training datasets are $|\mathcal{D}_s| = 47570$ and $|\mathcal{D}_w| = 1.5M$, while for validation and testing set, there are 14,313 and 10,526 images respectively. The confusion matrix between strong and weak labels are presented in Figure~\ref{fig:cm_strong_weak}.

\begin{figure}[t]
\begin{center}
\includegraphics[width=1.0\linewidth]{figure/cm_strong_weak_labels.pdf}
\end{center}
\caption{Confusion matrix between strong and weak labels. Grid numbers represent the percentage of confusion between true labels and weak labels. We ignore the elements whose values are less than $1\%$ for better demonstration. Frequency of each true label is listed at the top of each column.}
\label{fig:cm_strong_weak}
\end{figure}

@@

We also implement the bottom up method introduced in~\cite{sukhbaatar2014learning}. Briefly speaking, they proposed a noise model with the assumption that a weak label is only related to its true label. The relation is modeled by a confusion matrix $Q$ whose true value can be easily obtained as Figure~\ref{fig:cm_strong_weak} in our problem.

>>>>

\section{Label Noise Model} % (fold)
\label{sec:label_noise_model}
We target on the problem of learning a classifier from a set of images with noisy labels. To be specific, we have a noisy labeled dataset $\mathcal{D}_n=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes. Based on previous analysis of the noise types, we describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}. Despite the observed image $\vec{x}$ and the noisy label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the ground truth and the type of label noise, respectively. Both $\tilde{\vec{y}}$ and $\vec{y}$ are $L$-dimensional binary random variables in 1-of-$L$ fashion, \ie, only one element is equal to 1 while others are all 0.

@@

On the other hand, the latent variable $\vec{z}$ representing label noise type is also an 1-of-3 binary random variable. We assign three semantic meanings to each possible state of $\vec{z}$:
\begin{enumerate}
    \item The label is noise free, \ie, $\tilde{\vec{y}}$ should be equal to $\vec{y}$
    \item The label suffers from a pure random noise, \ie, $\tilde{\vec{y}}$ can take any possible value other than $\vec{y}$
    \item The label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are easily confused with $\vec{y}$
\end{enumerate}

Following this assignment rule, we define the conditional probability of the noisy label by
\begin{equation} \label{eq:likelihood}
    p(\tilde{\vec{y}}|\vec{y},\vec{z}) = \begin{cases}
        \mat{I}\vec{y} & \text{if } \vec{z}_1 = 1 \\
        \frac{1}{L-1}(\mat{U} - \mat{I})\vec{y} & \text{if } \vec{z}_2 = 1 \\
        \mat{C}\vec{y} & \text{if } \vec{z}_3 = 1
    \end{cases}
\end{equation}
where $\mat{I}$ is the identity matrix, $\mat{U}$ is the unit matrix (all the elements are one), and $\mat{C}$ is a sparse stochastic matrix with $\mathrm{tr}(\mat{C})=0$ and $\mat{C}_{ij}$ denoting the confusion probability between class $i$ and $j$. Then we can derive from Figure~\ref{fig:noise_pgm} the joint distribution of $\tilde{\vec{y}}, \vec{y}$ and $\vec{z}$ conditioning on $\vec{x}$:
\begin{equation} \label{eq:joint_distribution}
  p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}) = p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{y} | \vec{x}) p(\vec{z} | \vec{x})
\end{equation}

@@

To illustrate the relations between noisy label and ground truth, we can derive their conditional probability from Eq~\ref{eq:joint_distribution} by
\begin{equation}
    p(\tilde{\vec{y}} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}}, \vec{z} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{z} | \vec{x})
\end{equation}
which can be interpreted as a mixture model. Given an input image $\vec{x}$, the conditional probability $p(\vec{z} | \vec{x})$ can be seen as the prior of each mixture component. This makes a key difference between our work and~\cite{sukhbaatar2014learning}, where they assume $\tilde{\vec{y}}$ is conditionally independent with $\vec{x}$ if $\vec{y}$ is given. All the images share a same noise model in~\cite{sukhbaatar2014learning}, while in our approach each data sample has its own.

@@

For any probability distribution $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})$, we can derive a lower bound of the incomplete log-likelihood by
\begin{equation}
\begin{aligned}
    \log p(\tilde{\vec{y}} | \vec{x}; \theta) &= \log \sum_{\vec{y},\vec{z}} p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
    &\geq \sum_{\vec{y},\vec{z}} q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) \log \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)}{q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})}
\end{aligned}
\end{equation}
\textbf{E-Step} The difference between $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$ and its lower bound is the Kullback-Leibler divergence $\mathrm{KL}\left(q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) || p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)\right)$, which is equal to zero if and only if $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)$. Therefore, in each iteration $t$ of the E-Step, we first compute the posterior of latent variables using current parameters $\theta^{(t)}$:
\begin{multline} \label{eq:posterior}
    p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) = \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta^{(t)})}{p(\tilde{\vec{y}} | \vec{x}; \theta^{(t)})} \\
    = \frac{p(\tilde{\vec{y}}|\vec{y},\vec{z};\theta^{(t)}) p(\vec{y}|\vec{x};\theta^{(t)}) p(\vec{z}|\vec{x};\theta^{(t)})}{\sum_{\vec{y}',\vec{z}'} p(\tilde{\vec{y}}|\vec{y}',\vec{z}';\theta^{(t)}) p(\vec{y}'|\vec{x};\theta^{(t)}) p(\vec{z}'|\vec{x};\theta^{(t)})}
\end{multline}
Then the expected complete log-likelihood can be written as
\begin{equation}
    Q(\theta; \theta^{(t)}) = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)
\end{equation}
\textbf{M-Step} Since deep neural networks are exploited to model the probability $p(\vec{y}|\vec{x};\theta_1)$ and $p(\vec{z}|\vec{x};\theta_2)$, we perform gradient ascent on $Q$:
\begin{multline} \label{eq:gradient}
    \frac{\partial Q}{\partial \theta} = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta} \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
    = \sum_{\vec{y}} p(\vec{y} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta_1} \log p(\vec{y}|\vec{x};\theta_1) + \\
      \sum_{\vec{z}} p(\vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta_2} \log p(\vec{z}|\vec{x};\theta_2)
\end{multline}

@@

\subsection{Estimating the Matrix $\mat{C}$} % (fold)
\label{sub:confusion_estimation}
Notice that we do not set parameters to the conditional probability $p(\tilde{\vec{y}}|\vec{y},\vec{z})$ in Eq~\eqref{eq:likelihood} and keep it unchanged during the learning process. Because without other regularizations, learning all the three parts could lead to trivial solutions. For example, the network will always predict $\vec{y}_1 = 1$, $\vec{z}_3 = 1$, and the matrix $\mat{C}$ is learned to make $\mat{C}_{1i} = 1$ for all $i$. To avoid this degeneration, we choose to give $\mat{C}$ a good estimation while let the deep model learn to predict $p(\vec{y} | \vec{x})$ and $p(\vec{z} | \vec{x})$ for each input image.

We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy label. As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
\begin{equation}
    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N p(\tilde{\vec{y}}^{(N)}|\vec{y}^{(N)},\vec{z}^{(N)})
\end{equation}
Obviously, sample $i$ contributes nothing to the optimal $\mat{C}^*$ if $\vec{y}^{(i)}$ and $\tilde{\vec{y}}^{(i)}$ are equal. So that we ignore those samples and reinterpret the problem in another form by exploiting Eq~\ref{eq:likelihood}:
\begin{equation}
\begin{aligned}
\max_{\mat{C},\vec{t}} \quad & E=\sum_{i=1}^{N'} \log \alpha^{\vec{t}_i} + \log (\tilde{\vec{y}}^{(i)T} \mat{C} \vec{y}^{(i)})^{1-\vec{t}_i}\\
\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } K\times K \\
                    & \vec{t} \in \{0,1\}^{N'}
\end{aligned}
\end{equation}
where $\alpha=\frac{1}{L-1}$ and $N'$ is the number of remaining samples. The semantic meaning of the above formulation is that we need to assign each $(\vec{y},\tilde{\vec{y}})$ pair the optimal noise type, while finding the optimal $\mat{C}$ simultaneously.

@@

\section{Deep Learning from Noisy Labels} % (fold)
\label{sec:weak_label_deep_learning}
\begin{figure*}
\begin{center}
\includegraphics[width=0.9\linewidth]{figure/diagram.pdf}
\end{center}
\caption{System diagram of our proposed method. Two CNNs are exploited to predict object class $p(\vec{y}|\vec{x})$ and noise type $p(\vec{z}|\vec{x})$ respectively. A label noise model layer infers the ground truths according to CNNs' results and the observed noisy label. The ground truth is then used to supervise the CNNs. A separate strongly labeled dataset is also utilized to prevent the model from drifting away.}
\label{fig:framework}
\end{figure*}

We integrate the proposed label noise model into a deep learning framework. As demonstrated in Figure~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs. Moreover, we append a label-noise-model layer at the end, which takes as input the CNNs' prediction scores and the observed noisy label. Stochastic Gradient Ascent (SGA) with backpropagation technique is used to approximately optimize the whole network. In each forward pass, the label-noise-model layer computes the posterior of latent variables according to Eq~\eqref{eq:posterior}. While in the backward pass, it computes the gradients according to Eq~\eqref{eq:gradient}.

% The forward procedure is summarized in Algorithm~\ref{alg:forward}, and the backward pass for computing gradient with respect to $p(\vec{y}|\vec{x})$ is illustrated in Algorithm~\ref{alg:backward}.

% \begin{algorithm}
%     \SetKwData{Sum}{sum}
%     \SetKwFunction{Softmax}{Softmax}\SetKwFunction{Q}{Q}
%     \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}

%     \Input{Observed weak label vector $\tilde{\vec{y}}$ of size $N$}
%     \Input{Object class scores matrix $Y$ of size $N \times L$}
%     \Input{Noise type scores matrix $Z$ of size $N \times 3$}
%     \Output{Posterior probability matrix $P$ of size $L \times 3$}
%     \BlankLine

%     $P_y \leftarrow$ \Softmax{$Y$}\;
%     $P_z \leftarrow$ \Softmax{$Z$}\;
%     \BlankLine

%     \emph{\Q is the function that implements Eq~\eqref{eq:likelihood}}\;
%     \BlankLine

%     \For {$i \leftarrow 1$ \KwTo $N$} {
%         \Sum $\leftarrow 0$\;
%         \For {$j \leftarrow 1$ \KwTo $L$} {
%             \For {$k \leftarrow 1$ \KwTo $3$} {
%                 $P[i,j,k] \leftarrow P_y[i,j] \times P_z[i,k] \times$ \Q{$\tilde{\vec{y}}$,j,k}\;
%                 \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
%             }
%         }
%         $P[i,:,:] \leftarrow P[i,:,:] /$ \Sum\;
%     }

%     \caption{Forward pass}
%     \label{alg:forward}
% \end{algorithm}
% \begin{algorithm}
%     \SetKwData{Sum}{sum}
%     \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}

%     \Input{Object class scores matrix $Y$ of size $N \times L$}
%     \Input{Posterior probability matrix $P$ of size $L \times 3$}
%     \Output{Gradient matrix $\Delta_Y$ of size $N \times L$}
%     \BlankLine

%     \For {$i \leftarrow 1$ \KwTo $N$} {
%         \For {$j \leftarrow 1$ \KwTo $L$} {
%             \Sum $\leftarrow 0$\;
%             \For {$k \leftarrow 1$ \KwTo $3$} {
%                 \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
%             }
%             $\Delta_Y[i,:] \leftarrow \Delta_Y[i,:] + $ \Sum $\times Y[i,:]$\;
%             $\Delta_Y[i,j] \leftarrow \Delta_Y[i,j] - $ \Sum\;
%         }
%     }

%     \caption{Backward pass for computing gradient w.r.t. object class scores}
%     \label{alg:backward}
% \end{algorithm}

Directly training the whole network with random initialization is impractical, because the posterior computation could be totally wrong. Therefore, we need to pretrain each CNN component with strongly supervised data. Gathering ground truth object classes is straight forward, since we can just manually label some images by expert. The resulting strongly labeled dataset $\mathcal{D}_c$ can be directly used for training the network that predicts $p(\vec{y}|\vec{x})$. On the other hand, although off-the-shelf supervision for $p(\vec{z}|\vec{x})$ is not available, we can heuristically generate some data by utilizing the images having both strong and noisy labels. For each sample, we choose as ground truth the $\vec{z}$ that maximizes the likelihood in Eq~\eqref{eq:likelihood}.

After both the CNN components are properly pretrained, we can start training the whole network with massive noisy labeled data. However, some practical issues need to be further discussed. First, if we merely use noisy labels, we will lose precious knowledge that we have gained before and the model could be drifted. Therefore, we need to mix strongly label data together in to our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNN components. Then each CNN receives two kinds of gradients, one is from the strongly supervised data and the other is from the weakly supervised data. We denote them by $\Delta_c$ and $\Delta_n$, respectively. A potential problem is that $|\Delta_c| \ll |\Delta_n|$, because clean data is much less than the noisy data. To deal with this problem, we bootstrap the strongly labeled data $\mathcal{D}_c$ to half amount of the noisy data $\mathcal{D}_n$. This upsampling process brings another advantage --- the gradients we calculated in each mini-batch are much more stable.

Our proposed model has the ability to figure out the ground truth label given the image and its noisy label. From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how confusing is the input image itself. Label Propagation method~\cite{zhu2002learning} explicitly uses the first kind of information, while we implicitly capture it with a discriminative deep model. Meanwhile, we exploit the second kind of information to bridge the semantic gap between the image and its possible noisy labels.
% section weak_label_deep_learning (end)

@@

In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_c$), validation and testing sets. Meanwhile the remaining data construct the noisy labeled training dataset $\mathcal{D}_n$. A crucial data preprocessing step is to remove near duplicate images from $\mathcal{D}_c$ and $\mathcal{D}_n$, which ensures the reliability of our testing protocol. The size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 1.5M$, while validation and testing set consist of 14,313 and 10,526 images respectively. The confusion matrix between clean and noisy labels are presented in Figure~\ref{fig:cm_strong_weak}. We can see that the overall accuracy is only $61.54\%$, which means that the labels converted from surrounding text are quite noisy.

\begin{figure}[t]
\begin{center}
\includegraphics[width=1.0\linewidth]{figure/cm_strong_weak_labels.pdf}
\end{center}
\caption{\textbf{Confusion matrix between clean and noisy labels}. We hide extremely small grid numbers for better demonstration. Frequency of each true label is listed at the top of each column. The overall accuracy is $61.54\%$, which indicates that the noisy labels are not reliable.}
\label{fig:cm_strong_weak}
\end{figure}

@@

We also implement the bottom up method introduced in~\cite{sukhbaatar2014learning}. Briefly speaking, they proposed a noise model with the assumption that a noisy label is only related to its true label. The relation is modeled by a confusion matrix $Q$ whose values can be easily obtained as Figure~\ref{fig:cm_strong_weak} in our problem.
